Application of Micro-Rotors to Induce Crystal Nucleation: Challenges, Takeaways, and Future Prospects\\ PhD Thesis

### 2024-11-05 Latex_files/Thesis/chapters/chapter 1/main.tex
praveen commments plus chp 4 rework

\chapter{Introduction}
Crystallisation is one of the oldest forms of phase separation used by humanity\cite{Schoen1956}, put simply, it is the formation and growth 
of a new structured phase within a disordered bulk phase. This has 
applications in a number of industries such as pharmaceuticals, food 
production, and electronics \cite{Myerson2002}. Where the extraction 
of dilute materials can help improve product quality while keeping 
production costs low. The industrialisation of crystallisation has 
allowed engineers to reliably and efficiently induce the crystal 
formation within a bulk phase. However, while on a large scale 
crystallisation is seemingly an understood physical process, just a 
small amount of investigation into the literature reveals that at a 
micro scale there is yet to be unifying theory that can accurately 
explain the process of crystallisation \cite{Fu2021}. Of which there 
two primary areas of focus, nucleation and crystal growth. The latter 
focusing on how an already stable crystal grows and how it takes on its 
final shape. Whereas the former is more concerned with which factors 
contribute to its formation in order to control crystal growth.SW

In this chapter we will outline our current understanding of nucleation,
why there is a gap in the literature, and why there is still a need for
local control of nucleation events. Furthermore, we will also highlight
recent developments involving the use of optical tweezers (and other 
laser based methods) in order to develop our understanding of nucleation.
Lastly we highlight the connection between optical tweezer's ability to 
probe fluid viscosity via rotational motion, and the known link between
nucleation and fluid flow, to propose a novel potential method of 
creating localised nucleation events.

\section{Nucleation}
Nucleation is an example of a binary phase separation, where a dilute phase 
is miscible in a bulk phase, more often called the solute and solvent 
respectively. Because of thermodynamics, the two can only remain in 
equilibrium while below a specific concentration ($C_{eq}$) - below which 
the chemical potential $\mu$ for a miscible solution is greater than the 
potential required to separate the two phases. Once $C_{eq}$ is exceeded 
there is a chemical potential difference driving the solution to separate 
the two phases. Since different combinations of solute and solvent will 
have different equilibrium concentrations, researchers often instead measure 
the ratio between the solute and solvent by using 'supersaturation', one 
form of measuring supersaturation is shown below \cite{Mullin2001}:
\begin{align}
	\label{eq:supersaturation}
	S(T) = \frac{C_{sol}}{C_{eq}(T)}
\end{align}

Where $C_{sol}$ is just the solute concentration, and $C_{eq}(T)$is the 
equilibrium concentration at temperature $T$. While the solution remains 
supersaturated there is a chemical potential driving force for the solute 
to coalesce and separate from the solution as an ordered solid, the first 
formation of the crystal is referred to as the nucleus and understanding its 
formation of has been the focus of researchers for decades now. Typically, 
for an industrial crystallisation process the working principle is based on 
controlling and manipulating the supersaturation of the system. Of course 
nucleation events in a variety of different situations which each require 
their own classification.

@@

Where $J$ is the nucleation rate, $t_g$ is the 'growth time', $V$ is 
the volume of the individual samples, and $M^*(t)$ \& $M$ are the number 
of nucleated samples and the total number of samples used respectively.
While this is useful for studying the effects of different parameters at 
a small scale, for industrial applications there are to many external 
factors for primary nucleation to be the only

In contrast, secondary nucleation is the result of a initial 
seed crystal inducing further nucleation within the bulk solution
\cite{Botsaris1976}. The research of Secondary nucleation is 
fascinating for its own merits; is it speculated that the 
supersaturation barrier is non-existent \cite{Cashmore2022}, 
Furthermore control of secondary nucleation events are crucial 
for ensuring reliable industrial crystalliser performance, 
fig.~\ref{fig:secondary} depicts an attempt of classifying  
every possible mechanism that could lead to secondary nucleation.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.95\linewidth]{secondary_nucleation.jpg}
	\caption{Secondary Nucleation mechanisms, classified by Agrawal 
		and Paterson \cite{Agrawal2015}}
	\label{fig:secondary}
\end{figure}

Its clear that preventing secondary nucleation is impossible
with so many possible mechanism, modelling its contribution
to the nucleation rate has been the area of research for some
time now \cite{Cashmore2022, Flannigan2023}. In most cases 
secondary nucleation is actually desirable for large scale 
production as primary nucleation is a stochastic process.

\section{Nucleation Theories}
A number of potential theories have been proposed to explain 
how nucleation occurs at a microscopic scale. In doing so 
we could potentially predict the expected yield of a given
crystalliser based on the initial conditions of the 
solution. Outlined below are some of the most popular theories
currently used to describe nucleation.

\subsection{Classical Nucleation Theory (CNT)}
Sometimes referred to as 'Gibs Nucleation Theory' the original theory 
was first formed from the works of Volmer and Weber, and Frenkel 
\cite{Frenkel1939, Volmer1926}. While initially it was more focused 
into describing droplet formation in condensing vapours it was 
extrapolated to describe crystallisation. The central premise of 
classical theory is that nucleation occurs stochastically due to 
collisions between individual solute molecules, ions, or atoms. At the 
same time the bulk phase is resistant to the formation of a new phase. 
The competition between these random collisions and the bulk solution 
can be used to predict the probability of a newly formed nucleus.

@@

Where $v$ is the approximate volume of an individual molecule, $k_B$ is 
the Boltzmann constant, and $\sigma_{inf}$ is the interfacial tension of 
the bulk solution. This assumes that the nucleus will have a spherical 
morphology so that the surface tension $\sigma_{inf}$ is a scalar value. 
Looking at \eqref{eq:CNT} suggests that there must be some critical size 
$r$ where the free energy gain from the nucleus exceeds the surface tension 
of the surrounding fluid. Plotting the free energy of the system against 
nucleus size reveals a critical size above which the gain in free energy 
exceeds the interfacial tension. Furthermore it shows how increasing the 
supersaturation of the system reduces said barrier. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{Free_Energy_Diagram.png}
	\caption{Free energy diagram of a newly formed nucleus according 
		     to the Classical Nucleation Theory. The total free energy (blue)
		     is due to the competition between the volume free energy gain
		     (green) and the interfacial free energy cost (orange). Dotted
		     lines are for a higher supersaturation than the solid lines,
		     the interfacial energy cost is independent of supersaturation.}
	\label{fig:free_energy}
\end{figure}

@@

Where $A$ is a pre-factor that can be fine tuned to the exact demands
of the system (typically involving Zeldovich Factor, $Z$) the free 
energy barrier can be found by finding the turning point of $\Delta G_{tot}$.

@@

\subsection{Two Step Nucleation}
The two step nucleation theory is an extension to the CNT that suggests 
that prior to nucleation, the solute will cluster together. This was 
shown via colloid simulations showed that short range (such as in proteins \cite{Wolde1997, Gliko2005}) interactions allow for the formation of a liquid-liquid metastable phase from which a new solid phase could form \cite{Anderson2002, Karthika2016}. Several papers later reported the 
presence of stable liquid-like clusters that formed prior to nucleation \cite{Savage2009, Wolde1997, Soga1999}. The formation of these clusters 
can be understood by Oswald's rule; which says that any crystallising 
system does not immediately take the path to the lowest possible energy 
state but instead first transitions to the state with the smallest free 
energy barrier \cite{Ostwald1897}. Further phase transitions can still 
occur but this pathway minimises the overall free energy cost. Initially 
it was suspected that the formation of the dense liquid phase was a 
result of stochastic density fluctuations in the system. However, 
simulations suggest that the the local bond order is a stronger driving 
force than the local density \cite{Tan2013}. Studies into two step 
nucleation in Glycine solutions have noted that the solutions need to be 
aged before the presence of clusters was detected. This suggests that 
there exist further barriers to the formation of clusters in some systems,
this has lead to instead calling this phenomena as Multi-step Nucleation.

\subsection{Non-classical Nucleation} 
The current research into two step nucleation (or now more commonly 
referred to as multi-step nucleation theory) is developing a robust 
framework to describe what nucleation pathway will occur given the 
initial conditions. Reviews of all currently documented nucleation 
pathways identified highlighted the fact the need for a the 
development of \textit{in situ} techniques that can induce nucleation 
locally but can also reliably identify the nucleation pathway across 
a broad range of experimental conditions \cite{Karthika2016, Fu2021}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Crystallisation methods}
\subsection{Cooling Crystallisation}
For some binary mixtures the supersaturation is heavily dependent on 
the solution temperature, therefore a simple method of producing crystals 
is by cooling the mixture to induce crystal formation. At ambient 
temperatures the solute concentration is too high to be fully incorporated
into the solution ($S\gg 1$), after heating however the solute is fully 
dissolved into the solution ($S<1$). Now as the mixture is allowed to cool 
to room temperature the supersaturation will increase until crystal formation begins, the rate of cooling drastically influencing the size and number of crystals produced.

If $dT/dt$ is high then the final product will consist of large 
crystal and be low in number, as the nucleation rate is directly related
to the supersaturation only a handful of nuclei can form before the remaining
solute grows onto the surface. If $dT/dt$ is low then the final product will 
consist of smaller crystals and be far more numerous, as the supersaturation 
is so large that the new nuclei are forming continuously. Between these two 
extremes, one can define the meta-stable zone width, a region in the 
temperature-concentration phase space where both nucleation and crystal growth
can be reliably controlled. The lower limit being given by the solubility curve
of the binary mixture, and the upper limit being defined by the metastable zone.

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{MSZW.png}
	\caption{Typical Concentration vs Temperature plot with the solubility curve (black) and metastable zone (red). 3 different cooling curves are shown as well: a high rate of cooling (orange) shows the mixture quickly dropping below the solubility curve resulting in no new nuclei forming; a low rate of cooling (green) shows the mixture exceeding the metastable zone, where now nucleation occurs freely; and a typical cooling rate (blue) shows how a typical cooling crystalliser will operate, sitting in the middle of the other two curves.}
	\label{fig:MSZW}
\end{figure}

@@

\subsection{Evaporative Crystallisation}
In situations where control of the final product size or shape is not the main
focus, often the cheapest method of producing a crystalline product is simply
to allow the solvent evaporate and separate from the solute. Depending on the 
total volume of solvent to evaporate this process can take on time scale of 
several days to complete.

\subsection{Anti-solvent Crystallisation} 
Anti-solvent crystallisation is a more involved separation method ,
by adding a new solvent that is miscible with the old solvent but is 
immiscible with the solute, the solute's effective solubility is decreased.
As such, the solution becomes supersaturated. This has the trade off in that the overall mass ratio between the solvent and solute is now lower. Careful
measurement of the anti-solvent is required in order to ensure that the 
decrease in solubility is not out matched by the decrease in mass ratio.
Anti-solvent crystallisation is not as common due to the fact that not all
solutions will have an ideal anti-solvent candidate.

\section{Optical Tweezers}
\subsection{Background}
Optical tweezing has been a field of applied optics ever since the 1970s
when Ashkin \cite{Ashkin1970} first showed that focused light was capable 
of trapping micron sized particles due to light exerting 'radiation pressure'. 
The working principle was that a light source such as a laser could trap 
small objects within a 2D plane, as long as the light source had an 
approximately Gaussian profile. Soon after, Ashkin showed that the introduction 
of a microscope objective would allow one to focus the light source to a 
diffraction limited point that would stably trap small objects within a 
confined volume \cite{Ashkin1980}. This allowed Ashkin and others to study 
biological material and would later be used to probe microscopic properties 
such as the formation of colloidal aggregates \cite{Yi2021} to the drag 
forces exerted by a pure vacuum \cite{Ahn2018, Monteiro2018}. Due to the 
predictable behaviour of light, optical tweezers have become essential for 
measuring and exerting precise forces on the magnitude of pico-newtons 
allowing one to probe the material properties of the smallest materials.

\subsection{Gaussian Beams}
A Gaussian Beam is a simplistic approximation of a laser beam, in 
short it is an unbounded plane wave whose intensity of the 
electromagnetic field falls off from the centre similar to a normal distribution. This is perfectly fine for beams with a divergence 
angle of $0^{\circ}$, but later studies into focused beams showed 
that the assumption of a Gaussian intensity profile is inaccurate. 
A study conducted by Lock and Gouesbet found that as the Gaussian 
beam was focused the fall off in the electric field would 
consequentially induce additional electromagnetic fields 
\cite{Lock1994}. As a result the shape of the beam profile diverges 
from a Gaussian profile for focused beams. Regardless, for optical 
trapping experiments it is useful to assume a near Gaussian beam as 
many descriptions of lasers are simply combinations of plane waves 
(with varying amplitudes and wave vectors).  More information on 
electromagnetic theory is covered in chapter 2 but for now any 
mention of a focused laser can be thought of as a Gaussian beam, 
unless specified otherwise.

\subsection{Literature related to laser induced nucleation}
From as early as 1996 it has been known that laser irradiation is a viable
method of inducing nucleation within a supersaturated solution
\cite{Garetz1996}. The first reported case was notable as it used a 
1.064 $\mu m$ laser, the glycine solutions would appear transparent to
such a laser which would suggest there was no photo-chemical reaction.
Later studies into this phenomena found that the laser polarisation 
can influence the polymorph produced. With circularly polarised light 
producing $\alpha$-glycine and linearly polarised light forming
$\gamma$-glycine \cite{Garetz2002}. Future research has found nucleation 
can be induced by 1 of 3 routes.

\subsubsection{Non-Photochemical Laser Induced Nucleation}
Non-photochemical laser induced nucleation (NPLIN) involves irradiating 
a solution with a pulsed laser \cite{Garetz1996,Garetz2002,Sun2006}. 
The laser itself does not have to be heavily focused, instead irradiating
a large region of the solution all at once. The choice of laser is of
particular importance; with nucleation probability changing depending 
on the wavelength \cite{Kacker2017}. In addition, the choice of solute will 
effect the setup, not only because some solute's are unaffected, but also 
because there is a minimum laser threshold before nucleation is observed 
\cite{Garetz2002}. Several papers have debated the exact mechanism that 
induces NPLIN \cite{Garetz2002, Knott2011}. A suggested theory to this is 
an optical Kerr effect, for anisotropically charged solute molecules the 
electric field can reorient them to match the propagation direction 
\cite{Garetz2002}. If enough molecules are co-aligned the free energy 
barrier is reduced to allow for ambient nucleation \cite{Knott2011}. 
An alternative theory is the dielectric polarisation effect, in 
conditions that are unfavourable to cluster formation the polarising 
effect can stabilise the clusters \cite{Alexander2008}. As the cluster 
concentration rises so does the likelihood of nucleation \cite{Vekilov2010}. 
Both theories are similar to one another but where the optical Kerr theory
is limited to anisotropic solute molecules, the direct polarisation 
theory is more flexible. Regardless both theories struggle to explain
why the phenomena is not observed in all nucleation systems 
\cite{Korede2023}, such as acetamide which is similar to urea which 
does nucleate when irradiated \cite{Ward2016}. One of the benefits of 
NPLIN is that since the pulses are relatively low in their intensity 
they can be fired off quickly in succession, allowing for continuos 
crystallisation set ups. Overall, the NPLIN phenomena needs further 
research to properly describe its effects. The mean pulse intensity 
needs to be kept relatively low (on the order of $0.1-0.01 GW/cm^2$), 
as high intensity pulses lead to a completely different nucleation 
mechanism.

\subsubsection{High Intensity Laser Induced Nucleation}
High intensity laser induced nucleation (HILIN), where the pulse intensity 
is on the order of several $PW/cm^2$ is far simpler a mechanism to explain 
in comparison to NPLIN. The production of nuclei can be wholly associated 
to a cavitation process within the target solution, where the laser focus 
results in thermo-cavitation and the subsequent pressure wave leads to
a nucleation event around the focus of the laser \cite{Yoshikawa2005, 
Soare2011, Barber2019}. What remains in question is both how the physical 
properties (size, polymorph, etc) are influenced by the cavitation process, 
and how the pressure change triggers nucleation. The former has already 
been investigated; by adjusting the focal position Ikeda \textit{et al} 
could control the polymorph of indomethacin \cite{Ikeda2015}, this is not 
a universal method however, as it has also been shown that laser power can 
influence the crystal polymorph \cite{Wang2010}. The latter is a tricky 
task to address due to the fact that these cavitation bubbles form and 
collapse in less than $100\ \mu s$. Using fluorescence dyed proteins, 
researchers were able to observe a sudden spike in fluorescence just 
as the cavitation bubble began to collapse, they suggested that due 
to the collapse of the cavitation bubble the protein clusters are 
brought together at the lasers focal point. However, while the fluorescence 
imaging indicates a local concentration increase it is difficult to 
quantify this change depending on the size of the bubble \cite{Korede2023}. 
It has been suggested that in theory any solution can undergo HILIN 
\cite{Korede2023}, but proving such a theory requires a clear 
understanding of the phenomena both before and after cavitation occurs. 
Current research aims to combine experimental research with computer 
simulations to develop a universal theory, with the hope that this could 
also be related to NPLIN.

@@

Laser induced nucleation has the potential to be a viable method 
for \textit{in-situ} studying of nucleation events. Using high 
numerical aperture lenses one can localise the nucleation event 
to a specific region of the solution. The current issue is that 
the mechanism behind laser induced nucleation is not fully 
understood, as such it is rather difficult to modify the laser 
for different solution parameters. Instead it may be more 
effective to manipulate the solution using trapped particles. 
An common method is by apply a torque to a trapped particle, 
creating a micro-rotor that can can generate fluid flow.

>>>>

\chapter{Introduction}
Crystallisation is one of the oldest forms of phase 
separation used by humanity\cite{Schoen1956}, put 
simply, it is the formation and growth of a new 
structured phase within a disordered bulk phase. 
This has applications in a number of industries such 
as pharmaceuticals \cite{Gao2017}, food production 
\cite{Hartel2002}, and electronics \cite{Myerson2002}. 
Where the extraction of dilute materials can help 
improve product quality while keeping production costs 
low. The industrialisation of crystallisation has 
allowed engineers to reliably and efficiently induce 
the crystal formation within a bulk phase. However, 
while on a large scale crystallisation is seemingly an 
understood physical process, just a small amount of 
investigation into the literature reveals that at a 
micro scale there is yet to be unifying theory that can 
accurately explain the process of crystallisation 
\cite{Fu2021}. Crystallisation can be subdivided into 
two steps: Nucleation and Crystal growth. The latter 
focusing on how an already stable crystal grows and how 
it takes on its final shape. Whereas the former is more 
concerned with the first initial moments of a crystals 
formation within a bulk phase.

In this chapter we will outline our current understanding 
of nucleation,why there is a gap in the literature, and why 
there is still a need for local control of nucleation events. 
Furthermore, we will also highlight recent developments 
involving the use of optical tweezers (and other laser based 
methods) in order to develop our understanding of nucleation. 
Lastly we highlight the connection between optical tweezer's 
ability to probe fluid viscosity via rotational motion, and 
the known link between nucleation and fluid flow, to propose 
a novel potential method of creating localised nucleation events.

\section{Nucleation}
Nucleation is an example of a binary phase separation, 
where a dilute phase is miscible in a bulk phase, more 
often called the solute and solvent respectively. Because 
of thermodynamics, the two can only remain in equilibrium 
while below a specific concentration ($C_{eq}$) - below 
which the chemical potential $\mu$ for a miscible solution 
is greater than the potential required to separate the two 
phases. Once $C_{eq}$ is exceeded there is a chemical potential 
difference driving the solution to separate the two phases. 
Since different combinations of solute and solvent will 
have different equilibrium concentrations, researchers often 
instead measure the ratio between the solute and solvent by 
using 'supersaturation' \cite{Mullin2001}:
\begin{align}
	\label{eq:supersaturation}
	S(T) = \frac{C_{sol}}{C_{eq}(T)}
\end{align}

Where $C_{sol}$ is just the solute concentration, and 
$C_{eq}(T)$ is the equilibrium concentration at temperature 
$T$. While the solution remains supersaturated there 
is a chemical potential driving the solute to coalesce 
and separate from the solution as an ordered solid, the 
first formation of the crystal is referred to as the 
nucleus and understanding its formation has been the 
focus of researchers for decades now. Typically, for an 
industrial crystallisation process the working principle 
is based on controlling and manipulating the supersaturation 
of the system.

@@

Where $J$ is the nucleation rate, $t_g$ is the 'growth time', 
$V$ is the volume of the individual samples, and $M^*(t)$ \& 
$M$ are the number of nucleated samples and the total number 
of samples used respectively. While this is useful for studying
the effects of different parameters at a small scale, for
industrial applications there are to many external factors 
for primary nucleation to be measured accurately.

Secondary nucleation is the result of a initial seed crystal 
inducing further nucleation within the bulk solution 
\cite{Botsaris1976}. The seed crystals is often specially 
prepared ahead of time and added to a supersaturate solution. 
Due to interactions with the surrounding fluid and the container 
walls it is possible for the seed crystals to act as a surface
for further nucleation \cite{Anwar2015}. Control of secondary 
nucleation events are crucial for ensuring reliable industrial 
crystalliser performance. Fig.~\ref{fig:secondary} depicts an 
attempt of classifying every possible mechanism that could lead 
to secondary nucleation.
\begin{figure}[h!]
	\centering
	\includegraphics[width=0.95\linewidth]{secondary_nucleation.jpg}
	\caption{Secondary Nucleation mechanisms, classified by
		Agrawal and Paterson \cite{Agrawal2015}}
	\label{fig:secondary}
\end{figure}

This is not a universal classification system, there are a 
variety of opinions on how best to characterise different 
phenomena. It is heavily dependent on the theory used to 
describe nucleation events, this is accurate for both 
secondary and primary nucleation.

\section{Nucleation Theories}
Several potential theories have been proposed to explain 
how nucleation occurs at a microscopic scale. In doing so 
we could potentially predict the expected yield of a given
crystalliser based on the initial conditions of the solution. 
Outlined below are some of the most popular theories currently 
used to describe nucleation.

\subsection{Classical Nucleation Theory (CNT)}
Sometimes referred to as 'Gibbs Nucleation Theory' the 
original theory was first formed from the works of Volmer 
and Weber, and Frenkel \cite{Frenkel1939, Volmer1926}. 
While initially it was more focused on describing droplet
formation in condensing vapours it was extrapolated to 
describe crystallisation. The central premise of classical 
theory is that nucleation occurs stochastically due to 
collisions between individual solute molecules, ions, or 
atoms. At the same time the bulk phase is resistant to the
formation of a new phase. The competition between these 
random collisions and the bulk solution can be used to 
predict the probability of a newly formed nucleus.

@@

Where $S$ is the supersaturation from eq.~\eqref{eq:supersaturation} 
$v$ is the approximate volume of an individual molecule, 
$k_B$ is the Boltzmann constant, and $\sigma_{inf}$ is the 
interfacial tension of the bulk solution. This assumes that 
the nucleus will have a spherical morphology so that the 
surface tension $\sigma_{inf}$ is a scalar value. Looking at 
\eqref{eq:CNT} suggests that there must be some critical size 
$r$ where the free energy gain from the nucleus exceeds the 
surface tension of the surrounding fluid. This is reflected in 
fig.~\ref{fig:free_energy} where we plot the free energy of the 
system against nucleus size. This reveals a critical size above 
which the gain in free energy exceeds the interfacial tension. 
Furthermore fig.~\ref{fig:free_energy} shows how increasing the 
supersaturation of the system reduces said barrier. 
\begin{figure}[h!]
	\centering
	\includegraphics[width=\linewidth]{Free_Energy_Diagram.png}
	\caption{Free energy diagram of a newly formed nucleus according 
		     to the Classical Nucleation Theory. The total free energy (blue)
		     is due to the competition between the volume free energy gain
		     (green) and the interfacial free energy cost (orange). Dotted
		     lines are for a higher supersaturation than the solid lines,
		     the interfacial energy cost is independent of supersaturation.}
	\label{fig:free_energy}
\end{figure}

@@

Where $A$ is a pre-factor that can be fine tuned to the exact 
demands of the system, the free energy barrier can be found by finding 
the stationary point of $\Delta G_{tot}$.

@@

\subsection{Two Step Nucleation}
The two step nucleation theory is an extension to the CNT that suggests 
that prior to nucleation, the solute will cluster together. This has 
been shown via colloid simulations using protein molecules that have 
significant short range interactions \cite{Wolde1997, Gliko2005}. These 
interactions allow for the formation of a liquid-liquid metastable phase 
from which a new solid phase could form \cite{Anderson2002, Karthika2016}. 
Several papers later reported the presence of stable liquid-like clusters 
that formed prior to nucleation \cite{Savage2009, Wolde1997, Soga1999}. 
The formation of these clusters can be understood by Oswald's rule; which 
says that any crystallising system does not immediately take the path to 
the lowest possible energy state but instead first transitions to the state 
with the smallest free energy barrier \cite{Ostwald1897}. Further phase 
transitions can still occur but this pathway minimises the overall free 
energy cost. Initially it was suspected that the formation of the dense 
liquid phase was a result of stochastic density fluctuations in the system. 
However, simulations suggest that the the local bond order is a stronger 
driving force than the local density \cite{Tan2013}. Studies into two step 
nucleation in Glycine solutions have noted that the solutions need to be 
aged before the presence of clusters was detected \cite{Liao2022}. This 
suggests that there exist further barriers to the formation of clusters 
in some systems, this has lead to instead calling this phenomena as 
Multi-step Nucleation.

\subsection{Non-classical Nucleation} 
The current research into two step nucleation (or now more commonly 
referred to as multi-step nucleation theory) is developing a robust 
framework to describe what nucleation pathway will occur given the 
initial conditions. Reviews of all currently documented nucleation 
pathways highlighted the need for the development of \textit{in situ} 
techniques that can induce nucleation locally but can also reliably 
identify the nucleation pathway across a broad range of experimental 
conditions \cite{Karthika2016, Fu2021}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Crystallisation methods}
\subsection{Cooling Crystallisation}
For some binary mixtures the supersaturation is heavily dependent 
on the solution temperature, therefore a simple method of producing 
crystals is by cooling the mixture to induce crystal formation. At 
ambient temperatures the solute concentration is too high to be 
fully incorporated into the solution ($S\gg 1$), after heating however 
the solute is fully dissolved into the solution ($S<1$). Now as the 
mixture is allowed to cool to room temperature the supersaturation 
will increase until crystal formation begins, the rate of cooling 
drastically influences the size and number of crystals produced.

If $dT/dt$ is high then the final product will consist of large 
crystal and be low in number, as the nucleation rate is directly 
related to the supersaturation only a handful of nuclei can form 
before the remaining solute grows onto the surface. If $dT/dt$ is 
low then the final product will consist of smaller crystals and be 
far more numerous, as the supersaturation is so large that the new 
nuclei are forming continuously. Between these two extremes, one 
can define a meta-stable zone, a region in the temperature-
concentration phase space where both nucleation and crystal growth
can be reliably controlled. The lower limit being given by the 
solubility curve of the binary mixture, and the upper limit being 
defined by the point where crystals begin to spontaneously nucleate
within the solution.

\begin{figure}[h!]
	\includegraphics[width=\linewidth]{MSZW.png}
	\caption{Typical Concentration vs Temperature plot with the 
		solubility curve (black) and metastable zone (red). 3 
		different cooling curves are shown as well: a high rate 
		of cooling (orange) shows the mixture quickly dropping 
		below the solubility curve resulting in no new nuclei 
		forming. A low rate of cooling (green) shows the mixture 
		exceeding the metastable zone, where now nucleation occurs 
		spontaneously and cannot be controlled without further 
		cooling. A typical cooling rate (blue) shows how a 
		typical cooling crystalliser will operate, sitting in the 
		middle of the other two curves.}
	\label{fig:MSZW}
\end{figure}

@@

\subsection{Evaporative Crystallisation}
In situations where control of the final product size or shape 
is not the main focus, often the cheapest method of producing a 
crystalline product is simply to allow the solvent evaporate and 
separate from the solute. Depending on the total volume of solvent 
to evaporate this process can take on time scale of several days 
to complete. This is often used for the formation of seed crystals 
when larger seed crystals are required \cite{Srinivasan2008, Li1992}.

\subsection{Anti-solvent Crystallisation} 
Anti-solvent crystallisation is a more involved separation method,
by adding a new solvent that is miscible with the old solvent but 
is immiscible with the solute, the solute's effective solubility 
is decreased. As such, the solution becomes supersaturated. This 
has the trade off in that the overall mass ratio between the solvent 
and solute is now lower. Careful measurement of the anti-solvent is 
required in order to ensure that the decrease in solubility is not 
out matched by the decrease in mass ratio.Anti-solvent crystallisation 
is not as common due to the fact that not all solutions will have an 
ideal anti-solvent candidate.

\section{Optical Tweezers}
\subsection{Background}
Optical tweezing has been a field of applied optics ever since 
the 1980s when Ashkin \cite{Ashkin1970} first showed that focused 
light was capable of trapping micron sized particles due to light 
exerting 'radiation pressure'. The working principle was that a 
light source such as a laser could trap small objects within a 2D 
plane, as long as the light source had an approximately Gaussian 
profile (colloquially called a Gaussian beam). Soon after, Ashkin 
showed that the introduction of a microscope objective would allow 
one to focus the light source to a diffraction limited point that 
would stably trap small objects within a confined volume 
\cite{Ashkin1980}. This allowed Ashkin and others to study individual 
biological cells as the overall force was on the order of $10^{-12}\ 
N$ while being non-invasive to the internal structure. Later it would 
be used to probe microscopic properties such as the formation of 
colloidal aggregates \cite{Yi2021} to the drag forces exerted by a 
pure vacuum \cite{Ahn2018, Monteiro2018}. Due to the predictable 
behaviour of light, optical tweezers have become essential for 
measuring and exerting precise forces on the magnitude of pico-newtons 
allowing one to probe the material properties of the smallest materials.

\subsection{Literature related to laser induced nucleation}
From as early as 1996 it has been known that laser irradiation 
using a Gaussian beam is a viable method of inducing nucleation 
within a supersaturated solution \cite{Garetz1996}. The first 
reported case was notable as it used a 1.064 $\mu m$ laser, the 
glycine solutions would appear transparent to such a laser which 
would suggest there was no photo-chemical reaction. Later studies 
into this phenomena found that the laser polarisation can influence 
the polymorph produced. With circularly polarised light producing 
$\alpha$-glycine and linearly polarised light forming $\gamma$-glycine 
\cite{Garetz2002}. Future research has found nucleation can be 
induced by 1 of 3 routes.

\subsubsection{Non-Photochemical Laser Induced Nucleation}
Non-photochemical laser induced nucleation (NPLIN) involves 
irradiating a solution with a pulsed laser \cite{Garetz1996,
Garetz2002,Sun2006}. The laser itself does not have to be 
heavily focused, instead irradiating a large region of the 
solution all at once. The choice of laser is of particular 
importance; with nucleation probability changing depending 
on the wavelength. A study of KCl solutions found that for 
lower intensities it was found that nucleation was favoured 
for lower wavelengths but above a peak intensity of $5 MW/
cm^2$ the wavelength independence disappeared \cite{Kacker2017}. 
Measurements of the intensity prior and after irradiation 
confirmed this wavelength dependence was not due to any 
photo-chemical interactions \cite{Kacker2017}.

Additionally, the choice of solute will effect the setup, not 
only because some solute's are unaffected, but also because 
there is a minimum laser threshold before nucleation is observed 
\cite{Garetz2002}. Several papers have debated the exact mechanism 
that induces NPLIN \cite{Garetz2002, Knott2011}. A suggested 
theory to this is an optical Kerr effect: For anisotropically 
charged solute molecules the electric field can reorient them 
to match the propagation direction \cite{Garetz2002}. If enough 
molecules are co-aligned the free energy barrier is reduced to 
allow for ambient nucleation \cite{Knott2011}. An alternative 
theory is the dielectric polarisation effect, in conditions that 
are unfavourable to cluster formation the polarising effect can 
stabilise the clusters \cite{Alexander2008}. As the cluster 
concentration rises so does the likelihood of nucleation 
\cite{Vekilov2010}.

Both theories are similar to one another but where the optical 
Kerr theory is limited to anisotropic solute molecules, the 
direct polarisation theory is more flexible. Regardless both 
theories struggle to explain why the phenomena is not observed 
in all nucleation systems \cite{Korede2023}, such as acetamide 
which is similar to urea which does nucleate when irradiated 
\cite{Ward2016}. One of the benefits of NPLIN is that since the 
pulses are relatively low in their intensity they can be fired 
off quickly in succession, allowing for continuos crystallisation 
set ups. Overall, the NPLIN phenomena needs further research to 
properly describe its effects. The mean pulse intensity needs to 
be kept relatively low (on the order of $0.1-0.01 GW/cm^2$), as 
high intensity pulses lead to a completely different nucleation 
mechanism.

\subsubsection{High Intensity Laser Induced Nucleation}
High intensity laser induced nucleation (HILIN), where the pulse 
intensity is on the order of several $PW/cm^2$ is far simpler a 
mechanism to explain in comparison to NPLIN. The production of 
nuclei can be wholly associated to a cavitation process within 
the target solution, where the laser focus results in thermo-
cavitation and the subsequent pressure wave leads to a nucleation 
event around the focus of the laser \cite{Yoshikawa2005, Soare2011, 
Barber2019}.

What remains in question is both how the physical properties (size, 
polymorph, etc) are influenced by the cavitation process, and how 
the pressure change triggers nucleation. The former has already 
been investigated; by adjusting the focal position Ikeda \textit{et 
al} could control the polymorph of indomethacin \cite{Ikeda2015}, 
this is not a universal method however, as it has also been shown 
that laser power can influence the crystal polymorph \cite{Wang2010}. 
The latter is a tricky task to address due to the fact that these 
cavitation bubbles form and collapse in less than $100\ \mu s$. 
Using fluorescence dyed proteins, researchers were able to observe 
a sudden spike in fluorescence just as the cavitation bubble began 
to collapse, they suggested that due to the collapse of the cavitation 
bubble the protein clusters are brought together at the lasers focal 
point. However, while the fluorescence imaging indicates a local 
concentration increase it is difficult to quantify this change 
depending on the size of the bubble \cite{Korede2023}. It has been 
suggested that in theory any solution can undergo HILIN 
\cite{Korede2023}, but proving such a theory requires a clear 
understanding of the phenomena both before and after cavitation occurs. 
Current research aims to combine experimental research with computer 
simulations to develop a universal theory, with the hope that this 
could also be related to NPLIN.

@@

Laser induced nucleation has the potential to be a viable method 
for \textit{in-situ} studying of nucleation events. Using high 
numerical aperture lens one can localise the nucleation event 
to a specific region of the solution. The current issue is that 
the mechanism behind laser induced nucleation is not fully 
understood, as such it is rather difficult to modify the laser 
for different solution parameters. Instead it may be more 
effective to manipulate the solution using trapped particles. 
One way would to generate an optical torque on a trapped particle
and therefore shear the surrounding fluid, a method that is 
already in common use for micro-rheological studies \cite{Bishop2004, 
RobertsonAnderson2018}
